%-------------------------
% ATS-Friendly Resume in LaTeX
% Author: Jatin Rawat
% Optimized for ATS parsing & recruiter readability
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}

% ---- Margins ----
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.4in}

% ---- Page style ----
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% ---- URL styling ----
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ---- Accent color ----
\definecolor{accent}{RGB}{0, 79, 144}

% ---- Section formatting ----
\titleformat{\section}{
  \vspace{-4pt}\color{accent}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{accent}\titlerule \vspace{-4pt}]

% ---- List spacing ----
\setlist[itemize]{
  label=\textbullet,
  itemsep=1.5pt,
  topsep=2pt,
  leftmargin=0.22in,
  parsep=0pt
}

% ---- Custom commands ----
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{2pt}
  \begin{tabular*}{\textwidth}{@{}p{0.78\textwidth}@{\extracolsep{\fill}}r@{}}
    \textbf{#1} $|$ \small\textit{#2} & \small #3
  \end{tabular*}\vspace{-3pt}
}

% =========================================================
\begin{document}

% ===================== HEADER ============================
\begin{center}
  {\LARGE \textbf{JATIN RAWAT}} \\[5pt]
  \small
  +91 6395691500 \quad
  \href{mailto:jatinrawat072@gmail.com}{jatinrawat072@gmail.com} \quad
  \href{https://www.linkedin.com/in/jatin-rawat-744883282/}{linkedin.com/in/jatin-rawat-744883282}
\end{center}

\vspace{-10pt}

% ===================== EDUCATION =========================
\section{Education}
\resumeSubheading
  {Graphic Era Hill University}{Uttarakhand, India}
  {Bachelor of Technology in Computer Science and Engineering}{2023 -- Present}
\begin{itemize}
  \resumeItem{CGPA: \textbf{8.56 / 10.0}}
\end{itemize}

% ===================== PROJECTS ==========================
\section{Technical Projects}

\resumeProjectHeading
  {DocuShield -- Smart Regulatory \& Compliance Auditor}
  {Node.js, JavaScript, Pinecone DB, Gemini API, dotenv}
  {Jun 2026}
\begin{itemize}
  \resumeItem{Engineered a compliance-auditing RAG engine using \textbf{Gemini API} and \textbf{Pinecone} to automatically analyze corporate contracts, detect legal violations, and generate compliant clause rewrites.}
  \resumeItem{Designed and implemented a \textbf{Parent-Document Retrieval strategy} indexing small 2-sentence chunks (\textbf{text-embedding-004}) while dynamically mapping and returning full parent article context to the LLM to eliminate hallucinations.}
  \resumeItem{Developed a **custom local Vector Database** from scratch in JavaScript to compute **Cosine Similarity** math and handle persistent file-based indexing as a serverless fallback.}
  \resumeItem{Orchestrated index provisioning on Pinecone (Serverless AWS) and bulk vector streaming in optimized batch sizes, reducing manual legal audit cycles from hours to seconds.}
\end{itemize}

\vspace{2pt}

\resumeProjectHeading
  {AI-Code-Reviewer}
  {JavaScript, Node.js, GitHub API, Gemini API, Octokit}
  {Mar 2026}
\begin{itemize}
  \resumeItem{Engineered an automated AI-powered code review tool that analyzes repository files, detects issues, and programmatically commits fixes to GitHub using the \textbf{GitHub API}.}
  \resumeItem{Developed a feature to automatically apply AI-suggested improvements directly to source files, reducing manual debugging and fix time significantly.}
  \resumeItem{Utilized \textbf{Gemini API} for deep contextual analysis to identify logic flaws, security vulnerabilities, and code quality problems.}
  \resumeItem{Built an \textbf{agentic workflow} using tool-calling that recursively scans directories, reads and writes source files, and tracks modified files before each commit.}
\end{itemize}

% ===================== ACHIEVEMENTS ======================
\section{Achievements}
\begin{itemize}
  \resumeItem{Solved \textbf{500+ Data Structures and Algorithms (DSA)} problems across competitive programming platforms.}
  \resumeItem{\textbf{Codeforces Pupil} with a rating of \textbf{1280}; ranked \textbf{5730 out of 15,000+ participants} in a rated contest.}
  \resumeItem{\textbf{LeetCode}: Achieved a peak rank of \textbf{541 out of 20,000+ participants} in a Biweekly Contest (Top 600 globally).}
\end{itemize}

% ===================== TECHNICAL SKILLS ==================
\section{Technical Skills}
\begin{itemize}
  \resumeItem{\textbf{Programming Languages:} C++, Python, JavaScript, C}
  \resumeItem{\textbf{Web Development:} React, Node.js, Express.js, REST APIs, HTML, CSS}
  \resumeItem{\textbf{Generative AI:} RAG, Agentic Workflows, Prompt Engineering, LLM Integration, Vector Databases (Pinecone)}
  \resumeItem{\textbf{Tools \& Technologies:} Git, WebSocket, Docker, VS Code}
  \resumeItem{\textbf{Core CS Concepts:} Data Structures \& Algorithms, Object-Oriented Programming, Operating Systems, DBMS, Computer Networks}
\end{itemize}

% ===================== EXTRACURRICULAR ===================
\section{Extracurricular Activities}
\begin{itemize}
  \resumeItem{\textbf{Founding Member \& Team Lead}, Code Liners Community -- Led a team of \textbf{13 members} and mentored \textbf{100+ students} in competitive programming and software development.}
  \resumeItem{\textbf{Runner-up}, Intra-College Cricket Championship, competing among \textbf{16 teams}.}
\end{itemize}

\end{document}
